---
title: "JSON DQD Report"
output: 
  flexdashboard::flex_dashboard:
    orientation: columns
    vertical_layout: scroll
    theme: cosmo
 
---

<style>.main-container { max-width: 1200px; margin-left: 0; margin-right: auto; }</style>



``````{r global-options, include=FALSE}
# This section suppresses all code and errors so only charts, graphs, and tables are visible. 
knitr::opts_chunk$set(fig.width=12, fig.height=8, fig.path='figures/', echo=FALSE, warning=FALSE, message=FALSE, error=TRUE)



```


```{r setup, include=FALSE}
#load necessary packages for gauges, computation, reading JSON, etc
#install.packages("openxlsx")

   if (!require("pacman")) install.packages("pacman")
   library(pacman)
   pacman::p_load(tidyverse, flexdashboard, DT, knitr, flextable, openair, skimr,
                  data.table, rmarkdown, shiny, stringi, htmltools, janitor, 
                  DataExplorer, inspectdf, officer, 
                  openxlsx, readxl, writexl, outliers, curl)

# openxlsx package makes it easier to export multiple dataframes in R to Excel workbook with each dataframe in R corresponds to a worksheet in Excel


### NOTES FOR REUSABILITY###
#open code chunk that needs edited in a text editor (textEdit, notepad++, CorEditor, Sublime, etc), press ##needed or replace all

## EXAMPLE: 'total_dqd <- nrow(gedqd)
 #validity <- dplyr::filter(gedqd, dqd %in% "validity",)
 #total_validity <- nrow(validity)
 #percent_validity <- (total_validity / total_dqd) * 100
 #gauge(percent_validity, min = 1, max = 100, symbol = '%', gaugeSectors(
 #success = c(1, 100)))'

## CMD+F 'validity' and replace with 'consistencty' or other
```


```{r loadin}
#manually added dqd value pairs to each test in, and "column" names to first two tests in JSON #file

############# LOCAL CONFIGURATION #################
#setwd("")
###################################################

gedqd <- jsonlite::fromJSON("todds.json")   #use correct path for your data >  fromJSON("your.path")
expectations <- gedqd[["results"]][["expectation_config"]][["expectation_type"]]
success <- gedqd[["results"]][["success"]]
dqd <- gedqd[["results"]][["dqd"]]

column <- gedqd[["results"]][["expectation_config"]][["kwargs"]][["column"]]
df <- data.frame(expectations, success, dqd) 

gedqd <- cbind(column, df) #combines the 2 df's row to row 
consistency <- gedqd
#column and test name combined in a column
gedqd <- gedqd %>% 
  unite("Unique_Test", column:expectations, remove = FALSE)

#GEQDQ_Output <- write_xlsx(gedqd,"/Users/stephanie/Documents/Documents - Stephanie’s MacBook Pro/GEDQD_Output.xlsx")  #enter your path to save to locally

#GEDQD_csv <- write.csv(gedqd,"/Users/stephanie/Documents/Documents - Stephanie’s MacBook Pro/GEDQD_Output.csv")
##### CURRENTLY SET TO CHART STACK (SCROLLIING) - ADD TABSETS/PAGES ETC IF DESIRED

```

Data
===================================== 


-------------------------------------
```{r data-utilities}
std_border = fp_border(color = "black", width = 1)
```




### % of Tests Validity DQD
```{r validity}
total_dqd <- nrow(gedqd)
validity <- dplyr::filter(gedqd, dqd %in% "validity",)
total_validity <- nrow(validity)
percent_validity <- (total_validity / total_dqd) * 100

gauge(percent_validity, min = 1, max = 100, symbol = '%', gaugeSectors(
  success = c(1, 100)))



```


### % of Tests Consistency DQD
```{r consistency_gauge}
total_dqd <- nrow(gedqd)
consistency <- dplyr::filter(gedqd, dqd %in% "consistency",)
total_consistency <- nrow(consistency)
percent_consistency <- (total_consistency / total_dqd) * 100

gauge(percent_consistency, min = 1, max = 100, symbol = '%', gaugeSectors(
  success = c(1, 100)))

```


### % of Tests Completeness DQD
```{r completeness_gauge}

total_dqd <- nrow(gedqd)
completeness <- dplyr::filter(gedqd, dqd %in% "completeness",)
total_completeness <- nrow(completeness)
percent_completeness <- (total_completeness / total_dqd) * 100

gauge(percent_completeness, min = 1, max = 100, symbol = '%', gaugeSectors(
  success = c(1, 100)))

```

### Total Test Failure Rate
```{r Success_total_tests}

#percent of all tests failed
total_tests <- nrow(gedqd)
tests_failed <- dplyr::filter(gedqd, success %in% "FALSE",)
total_failed <- nrow(tests_failed)
percent_failed <- (total_failed / total_tests) * 100

gauge(percent_failed, min = 1, max = 100, symbol = '%', gaugeSectors(
  success = c(1, 100)))

```



### DQD Completeness Failure Rate
```{r completeness_success}



completeness_tests <- dplyr::filter(gedqd, dqd %in% "completeness",)
comp_total <- nrow(completeness_tests)
comp_tests_failed <- dplyr::filter(completeness_tests, success %in% "FALSE",)
comp_total_fail <- nrow(comp_tests_failed)
percent_comp_fail <- (comp_total_fail / comp_total) * 100

gauge(percent_comp_fail, min = 1, max = 100, symbol = '%', gaugeSectors(
success = c(1, 100)))

```


### DQD Validity Failure Rate
```{r validity_success}


validity_tests <- dplyr::filter(gedqd, dqd %in% "validity",)
val_total <- nrow(validity_tests)
val_tests_failed <- dplyr::filter(validity_tests, success %in% "FALSE",)
val_total_fail <- nrow(val_tests_failed)
percent_val_fail <- (val_total_fail / val_total) * 100

gauge(percent_val_fail, min = 1, max = 100, symbol = '%', gaugeSectors(
success = c(1, 100)))

```


### DQD Consistency Failure Rate
```{r consistency _success}


consist_tests <- dplyr::filter(gedqd, dqd %in% "consistency",)
consist_total <- nrow(consist_tests)
consist_tests_failed <- dplyr::filter(consist_tests, success %in% "FALSE",)
consist_total_fail <- nrow(consist_tests_failed)
percent_consist_fail <- (consist_total_fail / consist_total) * 100

gauge(percent_consist_fail, min = 1, max = 100, symbol = '%', gaugeSectors(
success = c(1, 100)))

```

```{r}

#list_of_datasets <-
  #list("validity" = validity, "consistency" = consistency)
## path = tempfile(fileext = ".xlxs"),
        #("Users/stephaniebeal/downloads/test.xlsx")



``` 

###